---
title: "Longtern_Rs_analysis"
output: html_document
---

## install and load packages
```{r preliminaries, message=TRUE, include=FALSE, echo=FALSE}
# Set chunks defaults; these options will be applied to all subsequent chunks
knitr::opts_chunk$set(results = 'hide', message = TRUE, include = TRUE, echo = FALSE,
                      fig.height = 4.5, fig.width = 8, cache = T)
# install.packages('cowplot')
# Load required packages
library(cowplot)
library(data.table)
library(ggplot2)
theme_set(theme_bw())
library(lubridate)
library(kableExtra)
library(cowplot)
# library(knitr)
library("ggpubr")
library(reshape)
# install.packages('Kendall')
library(zoo)
library(Kendall)
library(tidyr)
library(lubridate)
library(maps)
library(mapdata)
# devtools::install_github("bpbond/cosore")
# library(cosore)
library(lubridate)
# Source all needed functions
source('Rcode/functions.R')
# Much of this was presented at AGU 2018
library(readr)
library(lattice)
library(mblm)  # for Theil-Sen robust trend test
library(grid)
library(hexbin)
library(dplyr)
```


## prepare and load data
```{r load data}
plot_dir <- "outputs/agu_slides/"
# get data
srdb_v4 <- drake::readd(srdb_v4) 
srdb_v5 <- drake::readd(srdb_v5)
PT_Del <- read.csv('data/GlobalTempPrecipTimeSeries_Del.csv')
MGRsD = read.csv('data/MGRsD_SRDBV5.csv')
MGRsD %>% 
  filter(Rs_Norm > 0 & !is.na(Rs_Norm) & !is.na(MiddleClimate)) %>% 
  mutate(RsLog = log(Rs_Norm)) ->
  MGRsD
longterm <- drake::readd(longterm)
longterm <- longterm %>% filter(!is.na(X1))
longterm_Tm <- drake::readd(longterm_Tm)
IGBP <- read.csv("data/extdata/IGBP_Koppen_MODIS.csv")
left_join(srdb_v4, IGBP, by = c("Lat_Round" = "Latitude", "Long_Round" = "Longitude")) ->
  srdb_v4

srdb_v4 %>% 
  dplyr::select(Q10_all, MiddleClimate) %>% 
  filter(Q10_all < 10) %>% 
  na.omit() %>% 
  group_by (MiddleClimate) %>% 
  summarise(Q10_mean = mean(Q10_all), obs = n(), se = sd(Q10_all)/sqrt(obs)) ->
  srdb_v4_agg

# cosore data
cosore_all <- readRDS("data/cosore_all.rds")
cosore_site <- read.csv("data/csr_site.csv")
cosore_site$CSR_DATE_BEGIN <- as.Date(cosore_site$CSR_DATE_BEGIN, "%m/%d/%Y")
cosore_site$CSR_DATE_END <- as.Date(cosore_site$CSR_DATE_END, "%m/%d/%Y")

lm_results <- longtern_lm(longterm, longterm_Tm)
```



## Find long term (n>4) studies from srdb-v5 and MGRsD
```{r find out longterm studies from srdb}

# get study number from srdb_v5 which have more than 5 years of Rs measurement
# 10977 can be read from the fiture
study_exc <- c(1654,2298,2656,2927,3197,3254,3301,3302,3581,4174,4333,4564,4864,4938,
               5278,5519,5935,6347,6451,6504,6935,
               7290,7636,10266,
               # already in the longterm data
  
               # checked in srdb 
               467,864,1980,2018,2601,2926,2960,
               3390,4212,4234,4270,4979,5545,5984,6816,7087,
               7613,8699,8700,9845,10449,10624,10820,10951,10977,11054,11913,
               
               # checked in mgrsd
               4257,4883,5969,6576,7300,7659,9474,11083,11255,11878,11930,
               
               # checked github issue
               4333,4348,10614,10466,11054,
               
               # checked srdb by study_number and site_id
               1891,2056,2904,3053,4018,4442,4894,5162,5688,6438,6975,7634,8479,
               8534,10066,10483,10564,10910,11366)


## Find long term (n>4) studies from MGRsD
MGRsD %>% 
  dplyr::select(Study_number, Site_ID, Meas_Year) %>% 
  group_by(Study_number, Site_ID) %>% 
  count(Meas_Year) %>% 
  group_by(Study_number, Site_ID) %>% 
  summarise(n_year = n()) %>% 
  filter(n_year > 4) %>% 
  arrange(Study_number) %>% 
  filter(Study_number %!in% study_exc)

## Find long term (n>4) studies from srdb-v5
srdb_v5 %>% 
  filter(!is.na(Rs_annual)) %>% 
  dplyr::select(Rs_annual, Study_number, YearsOfData) %>% 
  count(Study_number, YearsOfData) %>% 
  filter(YearsOfData>=5 & Study_number %!in% study_exc)

srdb_v5 %>% 
  filter(!is.na(Rs_annual)) %>% 
  dplyr::select(Rs_annual, Study_number, Site_ID) %>% 
  count(Study_number, Site_ID) %>% 
  filter(Study_number %!in% study_exc) %>% 
  filter(n > 4)
```

## Plot long term sites spatial distribution
```{r site map, fig.height = 4, fig.width = 8}
# plot a site map for the long term data collected
# Step 2: Plot
# sort(unique(counties$region))
cosore_site %>% 
    filter(grepl('Rh', CSR_MSMT_VAR)) %>% 
    mutate(Latitude = CSR_LATITUDE,
           Longitude = CSR_LONGITUDE,
           count = year(CSR_DATE_END) - year(CSR_DATE_BEGIN),
           Data = "COSORE") %>% 
    dplyr::select(Latitude, Longitude, count, Data) ->
  csr_rh_site

bind_rows(
  MGRsD %>% 
    filter(!is.na(Rs_Norm)) %>% 
    dplyr::select(Latitude, Longitude, Meas_Year, Study_number) %>% 
    unique() %>% 
    group_by(Latitude, Longitude) %>% 
    summarise(count = n()) %>% 
    dplyr::select(Latitude, Longitude, count) %>% 
    mutate(Data = "DGRsD"),
  
  srdb_v4 %>% 
    filter(!is.na(Q10_all) & !is.na(Latitude)) %>% 
    mutate(Meas_Year = Study_midyear) %>% 
    dplyr::select(Latitude, Longitude, Meas_Year, Study_number) %>% 
    unique() %>% 
    group_by(Latitude, Longitude) %>% 
    summarise(count = n()) %>% 
    dplyr::select(Latitude, Longitude, count) %>% 
    mutate(Data = "SRDB"),
  
  csr_rh_site,
  
  longterm %>% 
    dplyr::select(Latitude, Longitude, count) %>% 
    mutate(Data = "Long-term")) ->
  map_sites


ggplot(data = map_data("world", region = ".", exact = FALSE)) + 
  geom_polygon(aes(x = long, y = lat, group = group),
               color = "white", fill = 'gray') + 
  guides(fill=FALSE) +
  geom_point(data = map_sites,
             aes(x=Longitude, y=Latitude,
                 size = count,
                 col = Data,
                 shape = Data),
             stroke = 1,
             alpha = 0.75) +
  geom_point(data = csr_rh_site,
    aes(x=Longitude, y=Latitude, size = count),
    col = "#F8766D", alpha = 0.75) +
  scale_shape_manual(values = c(16, 17, 1, 4)) +
  scale_x_continuous(name="Longitude", breaks=seq(-180,180, 60),labels = seq(-180,180, 60))+
  scale_y_continuous(limits = c(-60, 90),name="Latitude", breaks=seq(-60,90,30),labels = seq(-60,90,30)) +
  scale_size_continuous(name = "Years (n)") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) -> site_plot1

# only plot longterm sites
ggplot(data = map_data("world", region = ".", exact = FALSE)) + 
  geom_polygon(aes(x = long, y = lat, group = group),
               color = "white", fill = 'gray') + 
  guides(fill=FALSE) +
  geom_point(data = longterm,
             aes(x=Longitude, y=Latitude,
                 size = count),
             stroke = 1,
             col = "blue", alpha = 0.75) +
  scale_x_continuous(name="Longitude", breaks=seq(-180,180, 60),labels = seq(-180,180, 60))+
  scale_y_continuous(limits = c(-60, 90),
                     name="Latitude", breaks=seq(-60,90,30),
                     labels = seq(-60,90,30)) +
  scale_size_continuous(name = "Years (n)") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) -> site_plot2

site_plot2

```

## plot temperature annomaly
```{r, fig.width=8, fig.height=6}
# temperature annomaly time series
PT_Del %>% 
  ggplot(aes(Year, Tm_Annomaly)) +
  geom_bar(stat = "identity", alpha = 0.85, fill = "white", color = "black") +
  geom_smooth(color = "red", method = "lm", se = FALSE) +
  geom_smooth(color = "blue", method = "loess", se = FALSE, linetype = 2) +
  facet_wrap(~MiddleClimate, nrow = 4, scales = "free") +
  labs(x = "Year (1961-2014)", 
       y = expression(T[Air]~anomaly~(degree~C)))
# ggsave("outputs/FigureSX. T anomaly.jpg", width = 8, height = 6, dpi = 300, units = "in")
```


## plot Rs time series linear model results
```{r lm results}
lm_results$first_b %>% mean()
lm_results$n %>% mean()
lm_results$first_b_tm %>% mean()

lm_results %>% 
  ggplot(aes(x=first_b_tm, y=first_b)) +
  geom_point(aes(size = n), alpha = 0.75, col = "gray") +
  labs(x = expression(Slope~of~air~temperature~(degree~C~year^-1)),
       y = expression(Slope~of~soil~respiration~(g~C~m^-2~year^-1))) +
  geom_hline(yintercept = 0, linetype = "dashed",
             color = "red", size = 1) +
  geom_pointrange(aes(ymin = first_b - 2*first_b_se,
                      ymax = first_b + 2*first_b_se),
                  col = "gray",
                  show.legend = FALSE) +
  geom_smooth(mapping = aes(x=first_b_tm, y=first_b),
              method = "lm",
              se = T, fill = "skyblue",
              show.legend = FALSE) +
  guides(size = guide_legend("Year (n)")) -> plot_lm_results

## add average dot
lm_results_mean <- 
  tibble(tm_slope_mean = lm_results$first_b_tm %>% mean(),
         Rs_slope_mean = lm_results$first_b %>% mean(),
         Rs_slope_se_mean = lm_results$first_b_se %>% mean(),
         Year_mean = lm_results$n %>% mean())

plot_lm_results +
  geom_point(aes(x = tm_slope_mean, y = Rs_slope_mean),
             col = "black", size = 3.5, data = lm_results_mean) +
  geom_segment(aes(x = tm_slope_mean, y = Rs_slope_mean-2*Rs_slope_se_mean,
                   xend = tm_slope_mean, yend = Rs_slope_mean+2*Rs_slope_se_mean),
               col = "black", size = 1,
               data = lm_results_mean) -> plot_lm_results

plot_lm_results 

lm(first_b ~ first_b_tm, data = lm_results) %>% summary()
```

## plot Rs time series linear model results
### only plot results with p < 0.05
```{r lm plot2}
lm_results %>% 
  filter(p_b < 0.05 & first_b_tm > 0) -> lm_results_sub

lm_results_sub %>% 
  ggplot(aes(x=first_b_tm, y=first_b)) +
  geom_point(aes(size = n), alpha = 0.75, col = "gray") +
  labs(x = expression(Slope~of~air~temperature~(degree~C~year^-1)),
       y = expression(Slope~of~soil~respiration~(g~C~m^-2~year^-1))) +
  geom_hline(yintercept = 0, linetype = "dashed",
             color = "red", size = 1) +
  geom_pointrange(aes(ymin = first_b - 2*first_b_se,
                      ymax = first_b + 2*first_b_se),
                  col = "gray",
                  show.legend = FALSE) +
  geom_smooth(mapping = aes(x=first_b_tm, y=first_b),
              method = "lm",
              se = T, fill = "skyblue",
              show.legend = FALSE) +
  guides(size = guide_legend("Year (n)")) -> plot_lm_results_sub 

lm(first_b ~ first_b_tm, data = lm_results_sub) %>% summary()

## add average dot
lm_results_mean_sub <- 
  tibble(tm_slope_mean = lm_results_sub$first_b_tm %>% mean(),
         Rs_slope_mean = lm_results_sub$first_b %>% mean(),
         Rs_slope_se_mean = lm_results_sub$first_b_se %>% mean(),
         Year_mean = lm_results_sub$n %>% mean())

plot_lm_results_sub +
  geom_point(aes(x = tm_slope_mean, y = Rs_slope_mean),
             col = "black", size = 3.5, data = lm_results_mean_sub) +
  geom_segment(aes(x = tm_slope_mean, y = Rs_slope_mean-2*Rs_slope_se_mean,
                   xend = tm_slope_mean, yend = Rs_slope_mean+2*Rs_slope_se_mean),
               col = "black", size = 1,
               data = lm_results_mean_sub) -> plot_lm_results_sub

plot_lm_results_sub

```


## Possible reason 1 - need long time (~100 years) to observe a significant trend
There are measure variations during soil respiration measuring activities, and the variabilitty could generally seperated into two types: measure variability from interannual variability and from instantaneous variability.

### What's the SRDB interannual variability?
```{r srdb, echo=FALSE}
srdb_v5$Rs_interann_cv <- with(srdb_v5, Rs_interann_err / Rs_annual)
median_interann_cv <- median(srdb_v5$Rs_interann_cv, na.rm = TRUE)

srdb_v5 %>% 
  filter(!is.na(Rs_interann_cv)) -> srdb_v5_sub

srdb_v5 %>% 
  filter(!is.na(Rs_interann_cv)) %>% 
  ggplot(aes(x = Rs_interann_cv)) + 
  geom_histogram(bins = 30, fill = 'gray', col = "black") +
  scale_x_continuous(labels = scales::percent, limits = c(0, 1)) +
  geom_vline(xintercept = median_interann_cv, color = "red") +
  ylab("Count") + 
  xlab("CV between successive years") ->
  plot_annual_cv

plot_annual_cv
  
# save_agu_plot("srdb_cv.png")

```

OK, so the median measurement error here is ~`r round(median_interann_cv * 100, 0)`% for `r nrow(srdb_v5_sub)` observations of fluxes between `r round(min(srdb_v5_sub$Rs_annual, na.rm = T))` and `r round(max(srdb_v5_sub$Rs_annual, na.rm = T))` g C/m2/year.


### What's the CV within COSORE variability?

```{r cv12, echo = FALSE}
cosore_all %>% 
  mutate(ID_day = paste0(dset, "-", CSR_PORT, "-", year(CSR_TIMESTAMP_END),"-",
                         month(CSR_TIMESTAMP_END), "-", day(CSR_TIMESTAMP_END))) %>% 
  group_by(ID_day) %>%
  summarise(n = n(), meanFlux = mean(CSR_FLUX_CO2),
            cv = sd(CSR_FLUX_CO2) / mean(CSR_FLUX_CO2)) %>% 
  filter(n > 2) ->
  meas_error_1
median_error <- median(meas_error_1$cv)

ggplot(meas_error_1, aes(x = cv)) + 
  geom_histogram(bins = 30, fill = "gray", col = "black") +
  scale_x_continuous(labels = scales::percent, limits = c(-0.1, 1)) +
  geom_vline(xintercept = median_error, color = "red") +
  ylab("Count") + 
  xlab("CV between successive IRGA measurements") -> plot_IRGA_cv

plot_IRGA_cv
# save_agu_plot("licor12_cv.png")
```

OK, so the median measurement error here is ~`r round(median_error * 100, 0)`% for `r nrow(meas_error_1)` observations of fluxes between `r round(min(meas_error_1$meanFlux), 2)` and `r round(max(meas_error_1$meanFlux), 2)` µmol/m2/s.

## What if the meaure error was added to the soil respiration trend?
### Need to use data from Jian et al (2017) Earth's Future paper replace Hashimoto's data
```{r hashimoto, echo=FALSE}
library(ncdf4)
# Downloaded August 25, 2017 from http://cse.ffpri.affrc.go.jp/shojih/data/index.html
ncfiles <- c("data/extdata/RH_yr_Hashimoto2015.nc",
             "data/extdata/RS_yr_Hashimoto2015.nc")

nc <- nc_open(ncfiles[1])  # change to [1]
# These annual data start in 1901; extract 1990-2012
co2 <- ncvar_get(nc, "co2", start = c(1, 1, 1, 90), count = c(-1, -1, 1, 23))
nc_close(nc)

lattice::levelplot(co2[,,1])


co2 <- co2[400:600, 220:360,]  # punch a hole for testing: North America
# co2 <- co2[500:540, 320:360,]  # punch a hole for testing: part of North America

# below is a function for time series analysis
do_fitting <- function(co2) {
  
  f <- function(rh) { 
    df <- data.frame(x = seq_along(rh), y = rh)
    tryCatch(lm(y ~ x, data = df), error = function(e) NA)
  }
  
  # Fit linear model to each grid cell (this is slow)
  mods <- apply(co2, c(1, 2), FUN = f)  # slow
  
  # Extract slopes
  slopes <- apply(mods, c(1, 2), FUN = function(x) 
    if(!is.na(x)) x[[1]]$coefficients[["x"]] else NA)
  slopes <- matrix(slopes, nrow = nrow(mods), ncol = ncol(mods))
  
  # Extract slope p-values
  signif <- apply(mods, c(1, 2), FUN = function(x) 
    if(!is.na(x)) summary(x[[1]])$coefficients["x", "Pr(>|t|)"] else NA)
  signif <- matrix(signif, nrow = nrow(mods), ncol = ncol(mods))
  
  return(list(slopes = slopes, signif = signif))
}

# fitting and store at out
out <- do_fitting(co2)
summary(as.vector(out$slopes))

# plot out the fitting result
lattice::levelplot(out$slopes > 0)


lattice::levelplot(out$signif < 0.05)


ncells <- sum(!is.na(out$slopes))
pos_slope <- sum(out$slopes > 0, na.rm = TRUE)
signif_pos_slope <- sum(out$slopes > 0 & out$signif < 0.05, na.rm = TRUE)

lat_weight <- abs(cos(seq(-pi/2, pi/2, length.out = nrow(out$slopes))))
ncells_areawt <- sum(lat_weight * ncol(out$slopes))
pos_slope_areawt <- sum(out$slopes > 0 * lat_weight, na.rm = TRUE)
signif_pos_slope_areawt <- sum(out$slopes > 0 & out$signif < 0.05 * lat_weight, na.rm = TRUE)

# plot histgram
tibble(signif = as.vector(unlist(out$signif))) %>% 
  na.omit() %>% 
  ggplot(aes(x = signif)) + 
  geom_histogram(bins = 30, fill = "gray", col = "black") +
  # geom_vline(xintercept = 0.05, color = "red") +
  ylab("Count") + 
  xlab("p value of time series trend") ->
  plot_signif_before

plot_signif_before
```

Total cells = `r ncells`.

Cells with positive slope = `r pos_slope` or `r round(pos_slope / ncells * 100, 0)`%.

Cells with _significant_ positive slope = `r signif_pos_slope` or `r round(signif_pos_slope / ncells * 100, 0)`%.

Area with positive slope = `r round(pos_slope_areawt / ncells_areawt * 100, 0)`%.

Area with _significant_ positive slope = `r round(signif_pos_slope_areawt / ncells_areawt * 100, 0)`%.


## Re-do analysis with assumed error rate
```{r fuzz, echo=FALSE}

co2_fuzz <- fuzz(co2, error = median_error)
out_fuzz <- do_fitting(co2_fuzz)


lattice::levelplot(out_fuzz$slopes > 0)


lattice::levelplot(out_fuzz$signif < 0.05)


# plot histgram after cv added
tibble(signif = as.vector(unlist(out_fuzz$signif))) %>% 
  na.omit() %>% 
  ggplot(aes(x = signif)) + 
  geom_histogram(bins = 30, fill = "gray", col = "black") +
  # geom_vline(xintercept = 0.05, color = "red") +
  ylab("Count") + 
  xlab("p value of time series trend") ->
  plot_signif_after

plot_signif_after

ncells <- sum(!is.na(out_fuzz$slopes))
pos_slope <- sum(out_fuzz$slopes > 0, na.rm = TRUE)
signif_pos_slope <- sum(out_fuzz$slopes > 0 & out_fuzz$signif < 0.05, na.rm = TRUE)

lat_weight <- abs(cos(seq(-pi/2, pi/2, length.out_fuzz = nrow(out_fuzz$slopes))))
ncells_areawt <- sum(lat_weight * ncol(out_fuzz$slopes))
pos_slope_areawt <- sum(out_fuzz$slopes > 0 * lat_weight, na.rm = TRUE)
signif_pos_slope_areawt <- sum(out_fuzz$slopes > 0 & out_fuzz$signif < 0.05 * lat_weight, na.rm = TRUE)

# Convert to a data frame for ggplot2 plotting
ro = nrow(co2_fuzz)
co = ncol(co2_fuzz)
yr = dim(co2_fuzz)[3]
co2_fuzz_df <- tibble(
  flux = as.vector(co2_fuzz),
  lat = rep(seq_len(ro), times = co * yr),
  lon = rep(rep(seq_len(co), each = ro), times = yr),
  year = rep(seq_len(yr), each = ro * co),
  p = rep(as.vector(out_fuzz$signif), times = yr)
)

co2_fuzz_df %>% 
  filter(!is.na(p)) %>% 
  # pick a subset of grid cells for a readable plot
  distinct(lon, lat) %>% 
  sample_n(250) %>% 
  left_join(co2_fuzz_df, by = c("lon", "lat")) ->
  co2_fuzz_subsampled

co2_fuzz_subsampled %>% 
  ggplot(aes(year + 1990, flux, group = paste(lat, lon))) + 
  geom_line(color = "lightgrey") +
  xlab("Year") + ylab(expression(R[S]~(g~C~m^{-2}~yr^{-1}))) +
  geom_line(data = filter(co2_fuzz_subsampled, p < 0.05), color = "red", alpha = I(0.5)) ->
  fuzz_time_series

fuzz_time_series
# save_agu_plot("fuzz_over_time.png")
```

Cells with _significant_ positive slope (observations with `r round(median_error * 100, 0)`% measurement error) = `r signif_pos_slope` or `r round(signif_pos_slope / ncells * 100, 0)`%.

Area with _significant_ positive slope = `r round(signif_pos_slope_areawt / ncells_areawt * 100, 0)`%.


## Next steps
Next: make a nice graph of change over time <br>
using a subset of data for readability <br>
Convert array to data frame and plot rs versus time <br>
with a line for each grid cell <br>


## Simple: when would expect to see significance? toy-example
* We'd like to do this once for perfect data
* Once for data + interannual variability
* Once for data + iav + observational error

```{r simple toy-example, echo=FALSE}
set.seed(1234)

trend_emergence <- function(rd, theilsen = F) {
  Year <- seq_len(length(rd))
  trend_p <- rep(NA, length(rd))
  for(i in seq_along(trend_p)) {
    if(i > 2) {
      if(theilsen) {
        df <- tibble(Year = Year[1:i], rd = rd[1:i])
        suppressWarnings(m <- mblm::mblm(rd ~ Year, data = df))  # mblm doesn't like form below
      } else {
        m <- suppressWarnings(lm(rd[1:i] ~ Year[1:i]))
      }
      # Extract 2nd row (Year) and 4th column (Pr>[t] or Pr>|V|)
      trend_p[i] <- summary(m)$coefficients[2, 4]
    }
  }
  trend_p
}


# Temperature has risen 0.9 C in 40 years, more or less
dTdt <- round(0.9 / 40.0, 3)
q10 <- 2
R0 = 1.0
respdata <- tibble(Year = 1:100,
                   Temp = dTdt * Year,
                   Resp = R0 * q10 ^ (Temp / 10),
                   # This is interannual variability
                   Resp_iav = fuzz(Resp, 0.098),  # this is SRDB Rs_interannual_err
                   Resp_fuzz = fuzz(Resp_iav, median_error))

# Make a nice plot--first with ideal curve, 
p <- ggplot(respdata, aes(Year, Resp)) + 
  geom_point(color = "grey") + 
  ylab("Respiration") + coord_cartesian(ylim = c(0.75, 1.5)) + 
  annotate("text", 10, 1.4, label = paste("Q10 =", q10)) + 
  annotate("text", 10, 1.3, label = paste("dT/dt =", dTdt))
p

# then IAV
p <- p + geom_point(aes(y = Resp_iav))
p

# then observations
p <- p + 
  geom_errorbar(aes(ymin = Resp_iav - Resp_iav * median_error,
                    ymax = Resp_iav + Resp_iav * median_error))
p

# add idea trend line
p + geom_line(aes(y = Resp), color = "red", size = 2)

# add line with interannual variability
p + geom_line(aes(y = Resp), color = "pink", size = 2) +
  geom_line(aes(y = Resp_iav), color = "red", size = 2)

# add real soil respiration observation trend
p + geom_line(aes(y = Resp), color = "pink", size = 2) +
  geom_line(aes(y = Resp_iav), color = "pink", size = 2) +
  geom_line(aes(y = Resp_fuzz), color = "red", size = 2)

# creat a function for trend analysis
do_sim <- function(i, respdata, error = 0.0) {
  # This is observational error
  respdata$Resp_fuzz <- fuzz(respdata$Resp_iav, error)
  respdata$trend_p <- trend_emergence(respdata$Resp_fuzz)
  respdata
}

# run the analysis and store the results
results <- list()
library(parallel)
n_sims <- 100
results <- mclapply(seq_len(n_sims), do_sim, respdata, error = median_error)

# summary results
results %>% 
  bind_rows %>% 
  group_by(Year) %>% 
  summarise(n = n(), 
            Temp = mean(Temp), 
            Resp = mean(Resp),
            Resp_iav_sd = sd(Resp_iav),
            Resp_iav = mean(Resp_iav),
            Resp_fuzz_sd = sd(Resp_fuzz),          
            Resp_fuzz = mean(Resp_fuzz), 
            trend_p_sd = sd(trend_p), 
            trend_p = mean(trend_p)) %>% 
  filter(!is.na(trend_p)) ->
  results_summary

# plot the trend analysis result
p_TheilSen <- ggplot(results_summary, aes(Year, trend_p, color = trend_p < 0.05)) +
  geom_point() +
  geom_line(aes(y = Resp_fuzz)) +
  geom_line(aes(y = Resp), color = "grey") +
  geom_ribbon(aes(ymin = Resp_fuzz - Resp_fuzz_sd, 
                  ymax = Resp_fuzz + Resp_fuzz_sd, 
                  fill = trend_p < 0.05), color = NA, alpha = I(0.35)) +
  guides(color = FALSE, fill = FALSE) +
  annotate("text", 10, 1.5, label = paste("N =", n_sims)) +
  ylab("Theil-sen p-value   ///   Respiration")

print(p_TheilSen)
# save_agu_plot("simple_sim.png")
```



```{r, fig.height=8, fig.width=8}
# put figures together
plot_grid(fuzz_time_series, p_TheilSen,
          ncol = 1,
          labels = c("a", "b"))
```

```{r, fig.height=8, fig.width=8}
plot_grid(plot_IRGA_cv, plot_annual_cv) ->
  plot_cv
# put figures together
plot_grid(plot_signif_before, plot_cv, plot_signif_after,
          ncol = 1,
          labels = c("a", "b", "c"))
```


We then analyzed the trend of annual RS time series for all grid cells (n=`r ncells`). The results tuen out that about `r signif_pos_slope`% cells (Figure S7, panel a) showed a significant (p<0.05) possitive trend. However, in the field experiment, measurement error should be considered. We obtained the annual RS interannual variability from the newest version of global soil respiration database (SRDB-V5). In addition, we obtained the instantaneous RS flux measurement variability from a community database for continuous soil respiration and other soil-atmosphere greenhouse gas flux data (COSORE23). The results show that RS interannual variability is about `r round(median_interann_cv,2)*100`% of annual RS, and instantaneous RS flux measurement variability is about `r round(median_error, 2)*100`% of measurement mean (Figure S7, panel b). When RS measurement variability was considered, only ~`r round (signif_pos_slope / ncells * 100, 0)`% (Figure S7, panel c) of cells showed a significant increase trend.






